% $Id: publi.tex,v 1.16 2008/04/22 07:07:24 Moritz.Ringler Exp $
% Kein unabhängiges LaTeX-Dokument!
% Master-Dokument: diss.tex
%
% Versions-Informationen für diese Datei...
\RCS $Date: 2008/04/22 07:07:24 $ \RCS $Revision: 1.16 $
\RCS $Id: publi.tex,v 1.16 2008/04/22 07:07:24 Moritz.Ringler Exp $
%
\cleardoublepage
\bookmark[0]{Publikationen}{pub}
\begin{raggedright}
\addchap*{Zeitschriftenbeiträge zum Themenfeld dieser Dissertationsschrift}
\renewcommand{\labelenumi}{\roman{enumi}.}
\begin{enumerate}
\item M.~Ringler, A.~Schwemer, M.~Wunderlich, A.~Nichtl, K.~Kürzinger, T.~A. Klar
  und J.~Feldmann.
\href{http://dx.doi.org/10.1103/PhysRevLett.100.203002}{Shaping emission spectra of fluorescent
molecules with single plasmonic nanoresonators.}
\emph{Phys. Rev. Lett.} \textbf{100}(20), 203002 (2008).

\item M.~Ringler, T.~A. Klar, A.~Schwemer, A.~Susha, J.~Stehr, G.~Raschke, S.~Funk,
  M.~Borowski, A.~Nichtl, K.~Kürzinger, R.~T. Phillips und J.~Feldmann.
\href{http://dx.doi.org/10.1021/nl0712466}{{M}oving {N}anoparticles
  with {R}aman {S}cattering}.
\emph{Nano Lett.} \textbf{7}(9), 2753 (2007).

\item A.~Bek, R.~Jansen, M.~Ringler, S.~Mayilo, T.~A. Klar und J.~Feldmann.
\href{http://dx.doi.org/10.1021/nl072602n}{{F}luorescence
  {E}nhancement in {H}ot {S}pots of {A}{F}{M}-{D}esigned {G}old {N}anoparticle
  {S}andwiches}.
\emph{Nano Lett.} \textbf{8}(2), 485 (2008).

\item T.~Soller, M.~Ringler, M.~Wunderlich, T.~Klar, J.~Feldmann, H.-P. Josel,
  Y.~Markert, A.~Nichtl und K.~Kürzinger.
\href{http://dx.doi.org/10.1021/nl070623b}{{R}adiative and
  {N}onradiative {R}ates of {P}hosphors {A}ttached to {G}old {N}anoparticles}.
\emph{Nano Lett.} \textbf{7}(7), 1941 (2007).

\item E.~Dulkeith, M.~Ringler, T.~A. Klar, J. Feldmann, A.~Muñoz~Javier und W.~J.
  Parak.
\href{http://dx.doi.org/10.1021/nl0480969}{{G}old {N}anoparticles
  {Q}uench {F}luorescence by {P}hase {I}nduced {R}adiative {R}ate
  {S}uppression}.
\emph{Nano Lett.} \textbf{5}(4), 585 (2005).
\end{enumerate}

{\huge                     %
\sffamily\bfseries
Weitere Zeitschriftenbeiträge\\[16 pt]}
\begin{enumerate}
\setcounter{enumi}{5}
\item E.~V. Shevchenko, M.~Ringler, A.~Schwemer,
    D.~V. Talapin, T.~A. Klar, A.~L. Rogach, J.~Feldmann und A.~P. Alivisatos.
\href{http://dx.doi.org/10.1021/ja710619s}{%
Self-Assembled Binary Superlattices of CdSe and Au
    Nanocrystals and their Fluorescence Properties.}
\emph{J. Am. Chem. Soc.}  \textbf{130}(11), 3274 (2008).

\item A.~S. Susha, M.~Ringler, M.~Paderi, N. Li~Pira, G.~Carotenuto
und  A.~L. Rogach.
Luminescent gold films by thermolysis of gold-thiolate complexes in a polymer
matrix.
In Vorbereitung.

\item
T.~Soller, M.~Ringler, M.~Wunderlich, T.~A. Klar, J.~Feldmann,
H.-P. Josel, J.~Koci, Y.~Markert, A.~Nichtl und K.~Kürzinger.
Streptavidin Reduces Oxygen Quenching of Biotinylated Ruthenium(II) and
Palladium(II) Complexes.
In Vorbereitung.

\end{enumerate}

\renewcommand{\thefootnote}{\fnsymbol{footnote}} % Fußnoten auf Sternchen
                                                 % etc. umstellen
\cleardoublepage
%\bookmark[1]{Vorträge}{vortr}
\addchap*{Vorträge}

\begin{enumerate}
\item M.~Ringler, T.~A. Klar, G.~Raschke, A.~Schwemer und J.~Feldmann.
Optical manipulation of nanostructures built from organic molecules and gold
nanoparticles. Eingeladener Vortrag. \href{%
http://congress.phys.msu.ru/iconolat07/%
}{%
{\em International Conference on Coherent and Nonlinear Optics 2007}%
}, Minsk (Belarus).

\item M.~Ringler, T.~A. Klar, A.~Schwemer, J.~Stehr, G. Raschke und J. Feldmann,
A.~Nichtl und K.~Kürzinger, R.~T. Phillips. Surface-enhanced Raman scattering
(SERS) in single gold nanoparticle dimers. \href{%
http://mtin.de/DNA/molplasmon07/index.html%
}{%
{\em Molecular Plasmonics 2007}%
}, Jena.

\item M.~Ringler, T.~A. Klar\footnote{Vortragender},
A.~Schwemer, J.~Stehr, A.~Nichtl, K.~Kürzinger,
R.~T. Phillips und J.~Feldmann.
Surface-enhanced Raman scattering (SERS) in single gold nanoparticle dimers.
\href{%
http://spie.org/x14810.xml%
}{%
{\em European Conferences on Biomedical Optics 2007}%
}, München.

\addtocounter{footnote}{-1}% Fußnotenzähler dekrementieren. Wir wollen das
                           % gleiche Symbol nochmal
\item M.~Ringler, T.~Soller, M.~Wunderlich, Y.~Markert, H.~Josel, A.~Nichtl,
K.~Kürzinger, T.~A. Klar\footnotemark{} und J.~Feldmann.
Phosphorescence quenching in the vicinity of gold nanoparticles.
\href{%
http://spie.org/x14810.xml%
}{%
{\em European Conferences on Biomedical Optics 2007}%
}, München.

\item M.~Ringler, T.~A. Klar, A.~Schwemer, J.~Stehr, A.~Nichtl, K.~Kürzinger,
G.~Raschke, R.~T. Phillips und J.~Feldmann. Surface-enhanced Raman scattering
(SERS) in single gold nanoparticle dimers.
\href{%
http://regensburg07.dpg-tagungen.de/%
}{%
{\em DPG Frühjahrstagung 2007}
},
Regensburg.
\addtocounter{footnote}{-1}% Fußnotenzähler dekrementieren. Wir wollen das
                           % gleiche Symbol nochmal

\item T.~Soller, M.~Ringler\footnotemark{},
T.~A. Klar, J.~Feldmann, M.~Wunderlich, Y.~Markert, \mbox{H.-P.} Josel,
A.~Nichtl und K.~Kürzinger. Phosphorescence quenching in the vicinity of gold
nanoparticles.
\href{%
http://regensburg07.dpg-tagungen.de/%
}{%
{\em DPG Frühjahrstagung 2007}
}, Regensburg.

\item M.~Ringler, S.~Funk, M.~Borowski, T.~Soller,
A.~Susha, G.~Raschke, T.~A. Klar, and J.~Feldmann.
Spectroscopic properties of molecules in small gold-nanoparticle
aggregates.
\href{%
http://dresden06.dpg-tagungen.de/%
}{%
{\em DPG Frühjahrstagung 2006}
}, Dresden.

\item M.~Ringler, E.~Dulkeith, T.~A. Klar, J.~Feldmann,
A.~Mu\~{n}oz Javier und W.~J. Parak.
Gold Nanoparticles quench fluorescence by
phase induced radiative rate suppression.
{\em Bunsentagung 2005}, Frankfurt.

\item M.~Ringler, E.~Dulkeith, T.~A. Klar, J.~Feldmann, A.~Mu\~{n}oz Javier
und W.~J. Parak.
Distance dependence of fluorescence quenching by gold nanoparticles.
{\em DPG Frühjahrstagung 2005}, Berlin.

\item M.~Ringler, E.~Dulkeith, T.~Niedereichholz, T.~A. Klar und J.~Feldmann,
A. Mu\~{n}oz-Javier und W.~J. Parak. Fluorescence Lifetime Investigations of DNA mediated
Dye/Gold Nanoparticle Conjugates. {\em DPG Frühjahrstagung 2004}, Regensburg.

\item M.~Ringler. Fluorescence Lifetime Investigations of DNA mediated Dye/Gold
Nanoparticle Conjugates.
\href{%
http://www.nanoman.physik.uni-muenchen.de/special/specialneu.html%
}{%
{\em SFB~486 Manipulation von Materie auf der Nanometerskala, Workshop 2004}%
}, Ringberg.

\end{enumerate}
\end{raggedright}


