% $Id: prog.tex,v 1.5 2008/02/11 19:23:22 Moritz.Ringler Exp $
% Kein unabhaengiges LaTeX-Dokument!
% Master-Dokument: diss.tex
%
\definecolor{darkblue}{rgb}{0,0.08,0.45}
\maketitle

\section{About this document}
GMM-FIELD is a computer program that calculates the local electric field in an
aggregate of spherical particles that is hit by a plane light wave. Its companion
GMM-DIP calculates the absorbed and emitted power when a Hertzian dipole is placed
inside such an aggregate. Both programs were developed as part of my PhD thesis
\cite{phdrin08}, and I used them to calculate the theoretical results published in
\cite{bek07} and \cite{rin08}. This was possible only because Yu-Lin Xu
had published the source code of GMM and because Thomas Wriedt had kept it publicly
accessible on his Electromagnetic Scattering Programs web site \cite{wwwwriedt}.
Therefore, I decided to also publish the source code of GMM-FIELD and GMM-DIP
on the web.
Thomas Wriedt soon found out and included GMM-DIP and GMM-FIELD in his list of
scattering programs. Subsequently, he was asked about an English document that
describes how the programs can be used and he forwarded this
request to me. Lacking the time to write a comprehensive manual I agreed to
translate the relevant sections of my PhD thesis, and the result is the present
document. Please also read the GMM manual included in the original GMM package,
which is hosted on the Two Particle Scattering subpage of \cite{wwwwriedt}.
If you need further assistance using GMM-FIELD and GMM-DIP feel free to contact
me at gmm@momail.e4ward.com

\section{Bugs and fixes}
The original GMM-Field and GMM-DIP used a wrong normalization for the vector
spherical wave functions. This bug was discovered and fixed by Matthew Arnold, from UTS
Sidney, Australia. The fix has been included in the web release on 2009-07-13.
The bug does not affect the cross sections (GMM-FIELD) and rates (GMM-DIP) but will lead
to wrong results for the near field. In the cases that I have tested the
results with the bug are not far off from the correct ones. But there might be
cases where they are.

On 2014-01-16, another bug was found that might lead to incorrect higher-order
contributions to the near-field when the actual truncation order nmax(i) for one
of the other spheres/particles is greater than that of the first sphere/particle.
This bug was fixed in the web release on 2014-01-16.

GMM-FIELD and GMM-DIP are based on the 2001 GMM distribution and do
not contain any fixes from the 2003 version.

\section{Citing GMM-FIELD and GMM-DIP}
If you want to cite GMM-FIELD or GMM-DIP in a scientific article I would suggest
that you cite either \cite{phdrin08} or \cite{rin08}. Please also consider citing
Yu-Lin Xu's articles on the subject \cite{xuy95, xuy95err, xuy97, xuy98}. If you
want to tell your readers where to get the code I would suggest that you refer
them to the "Two particle scattering" subsection of \cite{wwwwriedt}.

\include{diss/anhang/prog/gmmf_en}
\include{diss/anhang/prog/gmmdip_en}
%\include{diss/anhang/prog/pda}

